\normalfont\spacedallcaps{Language reclamation: Literature review}

### 2023-06-25 assignment-4/article.tex
Format assignment 4 with latexindent

\begin{align*}
  \epsilon_j &= \frac{x_{t,i,j} - \sqrt{\alpha_t}x_i}{\sqrt{1-\alpha_t}} \\
   &= \frac{x_{t,i,j} - \sqrt{\alpha_t} \cdot \argmin_{x_k \in S^m} ||x_{t,i,j}-x_k||^2}{\sqrt{1-\alpha_t}} \\
  &= g^*_t(x_{t,i,j})
\end{align*}

@@

\begin{align*}
  \hat{L}_{S_t}(g^*_t) &= \frac{1}{m} \sum_{i=1}^{m} \sum_{j \in J} ||g^*_t (x_{t,i,j} ) - \epsilon_j ||^2 \\
  &= \frac{1}{m} \sum_{i=1}^{m} \sum_{j \in J} ||\epsilon_j - \epsilon_j ||^2 \\
  &= \frac{1}{m} \sum_{i=1}^{m} \sum_{j \in J} 0 = 0
\end{align*}

@@

\begin{align*}
  p_X(x) &= p_Z(z) \left|\frac{dz}{dx}\right| \\
  &= 1 \cdot \left| \frac{1}{2 \sqrt{x}} \right| = \frac{1}{2\sqrt{x}}
\end{align*}

@@

\begin{align*}
  p_X(x) &= p_Z(z) \left|\frac{dz}{dx}\right| \\
  &= \frac{1}{\sqrt{2\pi}} \exp \left[-\frac{1}{2}(\log(x(1-x)))^2 \right] \cdot \frac{|1-2x|}{x(1-x)}
\end{align*}

@@

\begin{align*}
  \phi &= \argmin \left[ \int \sum_{i=1}^I \delta[x-f[z_i,\phi]] \log \frac{\sum_{i=1}^I \delta[x-f[z_i,\phi]]}{\kappa q(x)} dx \right] \\
  &= \argmin \left[ \int \sum_{i=1}^I \delta[x-f[z_i,\phi]] \log \frac{\sum_{i=1}^I \delta[x-f[z_i,\phi]]}{q(x)} dx - \log \kappa \int \sum_{i=1}^I \delta[x-f[z_i,\phi]] dx \right] \\
  &= \argmin \left[ \int \sum_{i=1}^I \delta[x-f[z_i,\phi]] \log \frac{\sum_{i=1}^I \delta[x-f[z_i,\phi]]}{q(x)} dx - \log \kappa \right]
\end{align*}

@@

\begin{align*}
  Var[x_t] &= Var[\sqrt{1-\beta_t}\cdot x_{t-1} + \sqrt{\beta_t} \cdot \epsilon_t] \\
  &= Var[\sqrt{1-\beta_t}\cdot x_{t-1}] + Var[\sqrt{\beta_t} \cdot \epsilon_t] \\
  &= (1-\beta_t) Var[x_{t-1}] + \beta_t Var[ \cdot \epsilon_t] \\
  &= (1-\beta_t) \textbf{I} + \beta_t \textbf{I} \\
  &= \textbf{I}
\end{align*}

@@

\begin{align*}
  \mathbb{E}[z] &= 0 \\
  Var[z] &= a^2 + b^2
\end{align*}

@@

\begin{align*}
  Var[z] &= Var[a \epsilon_1 + b \epsilon_2] \\
  &= a^2 Var[\epsilon_1] + b^2 Var[\epsilon_2] + 2ab Cov[\epsilon_1, \epsilon_2] \\
  &= a^2 Var[\epsilon_1] + b^2 Var[\epsilon_2] \\
  &= a^2 + b^2
\end{align*}

>>>>

\begin{align*}
	\epsilon_j & = \frac{x_{t,i,j} - \sqrt{\alpha_t}x_i}{\sqrt{1-\alpha_t}}                                              \\
	           & = \frac{x_{t,i,j} - \sqrt{\alpha_t} \cdot \argmin_{x_k \in S^m} ||x_{t,i,j}-x_k||^2}{\sqrt{1-\alpha_t}} \\
	           & = g^*_t(x_{t,i,j})
\end{align*}

@@

\begin{align*}
	\hat{L}_{S_t}(g^*_t) & = \frac{1}{m} \sum_{i=1}^{m} \sum_{j \in J} ||g^*_t (x_{t,i,j} ) - \epsilon_j ||^2 \\
	                     & = \frac{1}{m} \sum_{i=1}^{m} \sum_{j \in J} ||\epsilon_j - \epsilon_j ||^2         \\
	                     & = \frac{1}{m} \sum_{i=1}^{m} \sum_{j \in J} 0 = 0
\end{align*}

@@

\begin{align*}
	p_X(x) & = p_Z(z) \left|\frac{dz}{dx}\right|                                 \\
	       & = 1 \cdot \left| \frac{1}{2 \sqrt{x}} \right| = \frac{1}{2\sqrt{x}}
\end{align*}

@@

\begin{align*}
	p_X(x) & = p_Z(z) \left|\frac{dz}{dx}\right|                                                                 \\
	       & = \frac{1}{\sqrt{2\pi}} \exp \left[-\frac{1}{2}(\log(x(1-x)))^2 \right] \cdot \frac{|1-2x|}{x(1-x)}
\end{align*}

@@

\begin{align*}
	\phi & = \argmin \left[ \int \sum_{i=1}^I \delta[x-f[z_i,\phi]] \log \frac{\sum_{i=1}^I \delta[x-f[z_i,\phi]]}{\kappa q(x)} dx \right]                                                   \\
	     & = \argmin \left[ \int \sum_{i=1}^I \delta[x-f[z_i,\phi]] \log \frac{\sum_{i=1}^I \delta[x-f[z_i,\phi]]}{q(x)} dx - \log \kappa \int \sum_{i=1}^I \delta[x-f[z_i,\phi]] dx \right] \\
	     & = \argmin \left[ \int \sum_{i=1}^I \delta[x-f[z_i,\phi]] \log \frac{\sum_{i=1}^I \delta[x-f[z_i,\phi]]}{q(x)} dx - \log \kappa \right]
\end{align*}

@@

\begin{align*}
	Var[x_t] & = Var[\sqrt{1-\beta_t}\cdot x_{t-1} + \sqrt{\beta_t} \cdot \epsilon_t]      \\
	         & = Var[\sqrt{1-\beta_t}\cdot x_{t-1}] + Var[\sqrt{\beta_t} \cdot \epsilon_t] \\
	         & = (1-\beta_t) Var[x_{t-1}] + \beta_t Var[ \cdot \epsilon_t]                 \\
	         & = (1-\beta_t) \textbf{I} + \beta_t \textbf{I}                               \\
	         & = \textbf{I}
\end{align*}

@@

\begin{align*}
	\mathbb{E}[z] & = 0         \\
	Var[z]        & = a^2 + b^2
\end{align*}

@@

\begin{align*}
	Var[z] & = Var[a \epsilon_1 + b \epsilon_2]                                            \\
	       & = a^2 Var[\epsilon_1] + b^2 Var[\epsilon_2] + 2ab Cov[\epsilon_1, \epsilon_2] \\
	       & = a^2 Var[\epsilon_1] + b^2 Var[\epsilon_2]                                   \\
	       & = a^2 + b^2
\end{align*}
